---
title: "MLMI simulations"
author: "Jonathan Bartlett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 2
  pdf_document: 
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
---

This document prints the results of simulations performed in the paper 'Maximum likelihood multiple imputation: Imputation can work without posterior draws' by Von Hippel and Bartlett.

# Y on X analysis model

## RMSE of estimates

```{r, echo=FALSE}

load(file=paste("simResults_yonx_",1, ".RData", sep=""))

missPropLevels <- c(25,50)
missMecLevels <- c("MCAR", "MAR")
MLevels <- c(10, 50, 200)

methodNames <- c("PDMI WB", "PDMI SB Res Var", "PDMI SB bivar", 
  "MLMI WB", "MLMI WB res var", "MLMI WB bivar", "MLMI SB Res Var", "MLMI SB bivar",
  "PDMI Boot", "MLMI Boot")

methodsToPrint <- c(1, 4, 9, 10)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(100*(sqrt(mean((ests[j,k,l,,methodsToPrint[i]]-0.5)^2))/0.5),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## % RMSE of SE estimates

```{r, echo=FALSE}

methodsToPrint <- c(2, 7, 1, 4, 9, 10)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(100*(sqrt(mean((se[j,k,l,,methodsToPrint[i]]-sd(ests[j,k,l,,methodsToPrint[i]]))^2))/sd(ests[j,k,l,,methodsToPrint[i]])),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## % Mean length of 95% CIs

```{r, echo=FALSE}

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## Mean(SE)/empirical SE for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(mean(se[j,k,l,,methodsToPrint[i]])/sd(ests[j,k,l,,methodsToPrint[i]]),2)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Mean CI length (coverage) for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Median degrees of freedom for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(median(df[j,k,l,,methodsToPrint[i]]),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## Mean(SE)/empirical SE for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(mean(se[j,k,l,,methodsToPrint[i]])/sd(ests[j,k,l,,methodsToPrint[i]]),2)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Mean CI length (coverage) for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Median degrees of freedom for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(median(df[j,k,l,,methodsToPrint[i]]),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


# X on Y analysis model

## RMSE of estimates

```{r, echo=FALSE}

load(file=paste("simResults_yonx_",0, ".RData", sep=""))

missPropLevels <- c(25,50)
missMecLevels <- c("MCAR", "MAR")
MLevels <- c(10, 50, 200)

methodsToPrint <- c(1, 4, 9, 10)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(100*(sqrt(mean((ests[j,k,l,,methodsToPrint[i]]-0.5)^2))/0.5),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## % RMSE of SE estimates

```{r, echo=FALSE}

methodsToPrint <- c(2, 7, 1, 4, 9, 10)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(100*(sqrt(mean((se[j,k,l,,methodsToPrint[i]]-sd(ests[j,k,l,,methodsToPrint[i]]))^2))/sd(ests[j,k,l,,methodsToPrint[i]])),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## % Mean length of 95% CIs

```{r, echo=FALSE}

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## Mean(SE)/empirical SE for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(mean(se[j,k,l,,methodsToPrint[i]])/sd(ests[j,k,l,,methodsToPrint[i]]),2)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Mean CI length (coverage) for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Median degrees of freedom for different WB approaches

```{r, echo=FALSE}

methodsToPrint <- c(4,5,6)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(median(df[j,k,l,,methodsToPrint[i]]),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```


## Mean(SE)/empirical SE for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(mean(se[j,k,l,,methodsToPrint[i]])/sd(ests[j,k,l,,methodsToPrint[i]]),2)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Mean CI length (coverage) for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- paste(round(mean(ci[j,k,l,,methodsToPrint[i],2]-ci[j,k,l,,methodsToPrint[i],1]),2), "(", round(100*(mean((ci[j,k,l,,methodsToPrint[i],1]<0.5) & (ci[j,k,l,,methodsToPrint[i],2]>0.5))-0.95),1), ")", sep=" ")
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```

## Median degrees of freedom for different SB approaches

```{r, echo=FALSE}

methodsToPrint <- c(2, 3, 7, 8)

resTable <- array(0, dim=c(12, length(methodsToPrint)+3))

j <- 0
rowNum <- 1
for (missProp in missPropLevels) {
  j <- j + 1
  k <- 0
  for (missMec in missMecLevels) {
    k <- k + 1
    l <- 0
    for (M in MLevels) {
      l <- l + 1
      p <- missProp/100
      
      resTable[rowNum,1] <- missProp
      resTable[rowNum,2] <- missMec
      resTable[rowNum,3] <- M

      for (i in 1:length(methodsToPrint)) {
        resTable[rowNum,i+3] <- round(median(df[j,k,l,,methodsToPrint[i]]),1)
      }
      rowNum <- rowNum + 1
    }
  }
}

colnames(resTable) <- c("Miss. %", "Miss. mec.", "Imputations", methodNames[methodsToPrint])
knitr::kable(resTable)

```
